Global code motion of congruent instructions

### 2017-04-17 paper.tex
code size at -Os

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|}
      \hline
% TODO: Check if putting code-size or spills number is okay or only %age is required.
% llvm trunk vs. llvm trunk with code-motion
Benchmark       &\% change in performance & \% change in codesize \\\hline
400.perlbench	& 1.00  & 1.00 \\\hline
401.bzip2	& 1.00  & 1.00 \\\hline
403.gcc	        & 1.00  & 1.01 \\\hline
429.mcf	        & 1.03  & 1.00 \\\hline
433.milc	& 1.00  & 1.00 \\\hline
444.namd	& 1.00  & 1.01 \\\hline
445.gobmk	& 0.99  & 1.01 \\\hline
447.dealII	& 0.95  & 1.01 \\\hline
450.soplex	& 0.99  & 0.99 \\\hline
453.povray	& 0.97  & 1.00 \\\hline
456.hmmer	& 0.99  & 1.00 \\\hline
458.sjeng	& 1.02  & 1.00 \\\hline
462.libquantum	& 1.00  & 1.00 \\\hline
464.h264ref	& 1.00  & 1.00 \\\hline
470.lbm	        & 1.00  & 1.00 \\\hline
471.omnetpp	& 1.00  & 0.99 \\\hline
473.astar	& 1.00  & 1.02 \\\hline
482.sphinx3	& 0.99  & 1.00 \\\hline
483.xalancbmk	& 1.01  & 0.99 \\\hline
Geomean         & 0.997 & 1.00 \\\hline
    \end{tabular}
  \end{center}
  \caption{Execution time and code size with and without code-motion on SPEC2006 at -Ofast}
  \label{tab:code-size}
\end{table}

>>>>

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|}
      \hline
% TODO: Check if putting code-size or spills number is okay or only %age is required.
% llvm trunk vs. llvm trunk with code-motion
Benchmark       &\% performance uplift (\%) at -Ofast & \% codesize uplift (\%) at -Ofast & codesize uplift (\%) at -Os\\\hline
400.perlbench	& 1.00  & 1.00 & 1.00\\\hline
401.bzip2	& 1.00  & 1.00 & 1.00\\\hline
403.gcc	        & 1.00  & 1.01 & 1.00\\\hline
429.mcf	        & 1.03  & 1.00 & 1.00\\\hline
433.milc	& 1.00  & 1.00 & 1.00\\\hline
444.namd	& 1.00  & 1.01 & 1.00\\\hline
445.gobmk	& 0.99  & 1.01 & 1.00\\\hline
447.dealII	& 0.95  & 1.01 & 0.98\\\hline
450.soplex	& 0.99  & 0.99 & 1.00\\\hline
453.povray	& 0.97  & 1.00 & 1.00\\\hline
456.hmmer	& 0.99  & 1.00 & 1.00\\\hline
458.sjeng	& 1.02  & 1.00 & 1.00\\\hline
462.libquantum	& 1.00  & 1.00 & 1.00\\\hline
464.h264ref	& 1.00  & 1.00 & 1.00\\\hline
470.lbm	        & 1.00  & 1.00 & 1.00\\\hline
471.omnetpp	& 1.00  & 0.99 & 1.00\\\hline
473.astar	& 1.00  & 1.02 & 1.00\\\hline
482.sphinx3	& 0.99  & 1.00 & 1.00\\\hline
483.xalancbmk	& 1.01  & 0.99 & 1.00\\\hline
Geomean         & 0.997 & 1.00 & 1.00\\\hline
    \end{tabular}
  \end{center}
  \caption{Execution time and code size with and without code-motion on SPEC2006.}
  \label{tab:code-size}
\end{table}
